Building the Torus Radiative Transfer Code

### 2008-09-19 torus/docs/how_to_build_torus.tex
Added make depends step.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@1339 25464f21-6099-402c-b30a-640f1d40d38b
fixes to disc_hydro_mod - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@1441 25464f21-6099-402c-b30a-640f1d40d38b

You can now go into the torus directory and build the code
%
\begin{verbatim}
$ cd torus
$ make
\end{verbatim}

@@

\begin{table}
  \begin{center}
    \begin{tabular}[|l|l|l|]{|l|l|l|}
\hline
    Option    & Description & Default \\
\hline
      pgplot  & link with pgplot libraries  & yes \\
      cfitsio & link with cfitsio libraries & yes \\
      debug   & switch on debugging flags   & no  \\
      profile & enable profiling            & no  \\
      static  & perform static linking      & no  \\
      trace   & use Intel trace collector   & no  \\
\hline
  \end{tabular}
\caption{Options which can be supplied to the make command when
  building torus.}
\label{table:make_options}
\end{center}
\end{table}

For example to build torus without linking to the pgplot libraries and
with debug flags enabled use
\begin{verbatim}
$ make pgplot=no debug=yes 
\end{verbatim}

>>>>

You can now go into the torus directory and build the code
%
\begin{verbatim}
$ cd torus
$ make depends
$ make
\end{verbatim}

@@

\begin{table}
  \begin{center}
    \begin{tabular}[|l|l|l|]{|l|l|l|}
\hline
    Option    & Description & Default \\
\hline
      cfitsio & link with cfitsio libraries & yes \\
      debug   & switch on debugging flags   & no  \\
      profile & enable profiling            & no  \\
      static  & perform static linking      & no  \\
      trace   & use Intel trace collector   & no  \\
\hline
  \end{tabular}
\caption{Options which can be supplied to the make command when
  building torus.}
\label{table:make_options}
\end{center}
\end{table}

For example to build torus without linking to the cfitsio libraries and
with debug flags enabled use
\begin{verbatim}
$ make cfitsio=no debug=yes 
\end{verbatim}
